### 2017-01-11 introduction.tex
Made article into a report
Adds details to introduction

\section{Introduction}

@@

@@

>>>>

\chapter{Introduction}

@@

The five paragraph essay, despite it's name, doesn't necessarily has five
literal paragraphs. It does however follow a structure of the form:

\begin{itemize}
    \item Introduction
    \item Exposure
    \item Arguments for
    \item Arguments against
    \item Conclusions
\end{itemize}

@@

Note that the number in \texttt{IND\_XXX} doesn't imply an order in the papers
listed in the document. Also, just because there is a paper in
\texttt{IND\_904} and a paper \texttt{IND\_906}, that doesn't imply that a
paper \texttt{IND\_905} needs to exists in the document.
